---
title: "Examples"
subtitle: "Folded output you can open."
description: "Cell output folded by the extension, one section per option, with the cell that produced each."
---

Every fold below was produced by the extension as this page was rendered.
The site sets these defaults in `_quarto.yml`:

```yaml
extensions:
  collapse-output:
    method: lua
    default-open: false
    summary-template: "{type} ({lines} lines)"
    summaries:
      stdout: "Console output"
      stderr: "Warnings and errors"
```

## Folding one cell

````markdown
```{r}
#| output-fold: true

summary(cars)
```
````

::: {.cell output-fold="true"}

```r
summary(cars)
```

::: {.cell-output .cell-output-stdout}

```
     speed           dist
 Min.   : 4.0   Min.   :  2.00
 1st Qu.:12.0   1st Qu.: 26.00
 Median :15.0   Median : 36.00
 Mean   :15.4   Mean   : 42.98
 3rd Qu.:19.0   3rd Qu.: 56.00
 Max.   :25.0   Max.   :120.00
```

:::

:::

The summary comes from `summaries.stdout`, which this site sets to "Console output".

## A summary of your own

````markdown
```{r}
#| output-fold: true
#| output-summary: "Click to view the model"

summary(lm(dist ~ speed, data = cars))
```
````

::: {.cell output-fold="true" output-summary="Click to view the model"}

```r
summary(lm(dist ~ speed, data = cars))
```

::: {.cell-output .cell-output-stdout}

```
Coefficients:
            Estimate Std. Error t value Pr(>|t|)
(Intercept) -17.5791     6.7584  -2.601   0.0123
speed         3.9324     0.4155   9.464 1.49e-12
```

:::

:::

`output-summary` beats both `summaries` and `summary-template`.

## Starting open

````markdown
```{r}
#| output-fold: true
#| output-open: true

head(cars, 3)
```
````

::: {.cell output-fold="true" output-open="true" output-summary="Already open"}

```r
head(cars, 3)
```

::: {.cell-output .cell-output-stdout}

```
  speed dist
1     4    2
2     4   10
3     7    4
```

:::

:::

`output-open` overrides the document's `default-open`, which is `false` here.

## Folding warnings and leaving results alone

`output-types` restricts folding to the kinds of output named.

```yaml
extensions:
  collapse-output:
    output-types: stderr
```

The `summaries.stderr` entry then labels them:

::: {.cell output-fold="true"}

```r
as.numeric("not a number")
```

::: {.cell-output .cell-output-stderr}

```
Warning message:
NAs introduced by coercion
```

:::

:::

## A template rather than fixed text

`summary-template` fills in `{type}` and `{lines}`, so a reader knows the size of what they are opening before they open it.

```yaml
extensions:
  collapse-output:
    summary-template: "{type} ({lines} lines)"
```

::: {.cell output-fold="true"}

```r
print(letters)
```

::: {.cell-output .cell-output-display}

```
 [1] "a" "b" "c" "d" "e" "f" "g" "h" "i" "j" "k" "l" "m"
[14] "n" "o" "p" "q" "r" "s" "t" "u" "v" "w" "x" "y" "z"
```

:::

:::

No entry in `summaries` covers `display` on this site, so the template is used instead.

## Folding everything

Rather than marking each cell, fold the lot and opt out where it matters:

```yaml
extensions:
  collapse-output:
    collapse-all-outputs: true
```

````markdown
```{r}
#| output-fold: false

plot(cars)
```
````

`output-fold: false` on a cell still wins, so a plot worth seeing stays visible.

Pair it with `auto-collapse-size` to fold only what is actually long:

```yaml
extensions:
  collapse-output:
    collapse-all-outputs: true
    auto-collapse-size: 20
```

Outputs of twenty lines or more are forced closed, whatever `default-open` says.

## Source

The repository ships a short, standalone starting point you can copy: [`example.qmd`](https://github.com/mcanouil/quarto-collapse-output/blob/main/example.qmd).
