---
title: "Examples in R"
subtitle: "The same folds, from the knitr engine."
description: "The collapse-output filter folding output from R cells, showing that it works on what Quarto emits rather than on any one engine."
engine: knitr
---

The [Examples](examples.qmd) page runs Python through Jupyter.
This one runs R through knitr, from the renv environment declared at the repository root.

The filter acts on the cell and cell-output elements Quarto emits, which are the same whichever engine produced them, so nothing here is configured differently.

## Folding one cell

```{r}
#| echo: fenced
#| output-fold: true

summary(cars)
```

The summary comes from `summary-template`, set once for the whole site, and its line count is measured from the output above.

## A summary of your own

```{r}
#| echo: fenced
#| output-fold: true
#| output-summary: "Click to view the model"

summary(lm(dist ~ speed, data = cars))
```

## Starting open

```{r}
#| echo: fenced
#| output-fold: true
#| output-open: true

head(cars, 3)
```

## Warnings and errors

```{r}
#| echo: fenced
#| output-fold: true

message("A message on the error stream.")
as.numeric("not a number")
head(cars, 3)
```

Output on the error stream is folded separately, under `summaries.stderr`, while the standard stream falls back to the template.

## Rich output

```{r}
#| echo: fenced
#| output-fold: true
#| output-summary: "The figure"

plot(cars, pch = 19, main = "Speed and stopping distance")
```

A plot is display output rather than console text, and is folded under its own type.

## Source

The repository ships a short, standalone starting point you can copy: [`example.qmd`](https://github.com/mcanouil/quarto-collapse-output/blob/main/example.qmd).
